Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks

### 2023-08-12 discussion/discussion.tex
Updates from Overleaf

@@

We argue whether factors such as the size of the representation layer and the size of the model \cite{verydeep} might be insufficient. Furthermore, we posit that the loss function could decrease further with additional time to iterate repeatedly over the dataset.

While our results may not yet rival state-of-the-art benchmarks, they affirm we're on the right path and reveal the potential of this research direction. Importantly, we've seen that progress doesn't have to be expensive—though time and potential copyright issues are considerations.

>>>>

One of the main reasons why \cite{deepfeaturesegment, SalamonDeepSegmentation} outperform our method might be their task-tailored designs specifically oriented towards music segmentation analysis (MSA). In contrast, our method aims to be broader and more abstract, which may present a downside when evaluating specific tasks.

@@

We argue whether factors such as the size of the representation layer and the size of the model \cite{verydeep} might be insufficient. Furthermore, we posit that the loss function could decrease further with additional time to iterate repeatedly over the stochastic and never-ending dataset.

While our results may not yet rival state-of-the-art benchmarks, they affirm we're on the right path and reveal the potential of this research direction. Importantly, we've seen that progress doesn't have to be expensive—though time and potential data copyright issues are considerations.

### 2023-08-12 evaluation/evaluation.tex
Updates from Overleaf

The developed model has been trained on GTZAN \cite{GTZAN} and the Million Song Dataset (MSD) \cite{MSD} and evaluated on the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS}.

\subsection{GTZAN dataset}
The GTZAN Genre Collection is a widely-used dataset for music genre classification tasks.

This dataset comprises 1,000 audio tracks that are each 30 seconds long. These tracks are evenly distributed across ten genres: blues, classical, country, disco, hip hop, jazz, metal, pop, reggae, and rock, each containing precisely 100 songs. The audio files are stored as WAV files with a sample rate of 22050 Hz \cite{GTZAN}.

@@

>>>>

The developed model has been trained on GTZAN \cite{GTZAN}, the Million Song Dataset (MSD) \cite{MSD} and evaluated on the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS}.

\subsection{GTZAN dataset}
The GTZAN Genre Collection is a widely-used dataset for music genre classification tasks. It comprises 1,000 audio tracks that are each 30 seconds long. These tracks are evenly distributed across ten genres: blues, classical, country, disco, hip hop, jazz, metal, pop, reggae, and rock, each containing precisely 100 songs. The audio files are stored as WAV files with a sample rate of 22050 Hz \cite{GTZAN}.

@@

Note: We used SALAMI's original release from 2011, featuring 1,359 tracks.

### 2023-08-12 introduction/Subsections/Previous work.tex
Updates from Overleaf

On the other hand, \cite{SalamonDeepSegmentation} explores using unsupervised deep learning methods for creating meaningful music representations and applying them to music structure analysis tasks. The research employs Convolutional Neural Networks (CNNs) trained on millions of tracks from a music streaming service. The study reveals that these embeddings, derived via unsupervised learning, are effective at capturing musical structures, particularly when integrated with traditional feature engineering methods.

@@

The results prove that unsupervised deep-learning techniques which derive audio embeddings offer more robust and efficient alternatives to traditional manual feature-engineering methods in music segmentation.

>>>>

While \cite{deepfeaturesegment} approach and ours are very similar, there are some contrastive differences worth mentioning. These nuances stem from how much the approaches are task-tailored: the authors train their model on a dataset of audio features labeled with their corresponding music segments. They use a sampling strategy to create positive and negative examples likely from the same or different music segments. The method by \cite{deepfeaturesegment} requires music with clear beats and onsets. The sampling strategy relies on the fact that beats or onsets typically separate music segments. If the music does not have clear beats or onsets, it will be difficult for the method to create positive and negative examples likely to be from the same or different music segments.

Our approach is slightly different in two ways. First, we use physical time as input data rather than audio features. Second, our triplet selection pipeline is more abstract and designed for broader music understanding scope -yet still to be evaluated- rather than specifically tailored to music segmentation.

On the other hand, \cite{SalamonDeepSegmentation} explores using unsupervised deep learning methods for creating meaningful music representations and applying them to music structure analysis tasks. The research employs the same kind of deep architecture trained on millions of tracks from a music streaming service. The study reveals that these embeddings, derived via unsupervised learning, are effective at capturing musical structures, particularly when integrated with traditional feature engineering methods and a multi-level section fusion algorithm to merge short sections into longer ones.

@@

The results prove that unsupervised deep-learning techniques which derive audio embeddings offer more robust and efficient alternatives to exclusively traditional manual feature-engineering methods in music segmentation.

### 2023-08-12 methods/subsections/implementation.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics{figures/images/applsci-08-00150-g003.png}
    \caption[SampleCNN filters]{The spectrum of the estimated filters in the intermediate layers of SampleCNN is sorted by the frequency of the peak magnitude. The x-axis represents the index of the filter, and the y-axis represents the frequency range from 0 to 11 kHz. The model used for visualization is  39---SampleCNN with 59,049 samples as input. Visualization was performed using the gradient ascent method to obtain the accumulated gradient-based input waveform-like signal that maximizes the activation of a filter in the layers. To effectively find the filter characteristics, we set the input size to 729 samples, close to a typical frame size.}
    \label{fig:filters}
\end{figure}

@@

\begin{table}[ht]
\centering
\small
\begin{tabularx}{\textwidth}{
  >{\centering\arraybackslash\hsize=0.4\hsize}X
  >{\centering\arraybackslash\hsize=0.2\hsize}X
  >{\centering\arraybackslash\hsize=0.2\hsize}X
  >{\centering\arraybackslash\hsize=0.2\hsize}X}
\toprule
\thead{\textbf{Layer Type}} & \thead{\textbf{In Channels}} & \thead{\textbf{Out Channels}} & \thead{\textbf{Num. of layers}} \\
\midrule
Conv + ReLU & 1 & 128 & 1 \\
Conv + BatchNorm + ReLU + MaxPool & 128 & 128 & 2 \\
 & 128 & 256 & 1 \\
 & 256 & 256 & 6 \\
 & 256 & 512 & 1 \\
Conv + BatchNorm + ReLU + AvgPool & 512 & 512 & 1 \\
Fully connected layer & 512 & 128 & 1 \\
\bottomrule
\end{tabularx}
\caption[SampleCNN layer specifications]{Layer specifications for our SampleCNN model implementation; extended from \cite{CLMR2021}.}
\label{tab:samplecnntable}
\end{table}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/images/applsci-08-00150-g003.png}
    \caption[SampleCNN filters]{\small{The spectrum of the estimated filters in the intermediate layers of SampleCNN is sorted by the frequency of the peak magnitude. The x-axis represents the index of the filter, and the y-axis represents the frequency range from 0 to 11 kHz. The model used for visualization is  39---SampleCNN with 59,049 samples as input. Visualization was performed using the gradient ascent method to obtain the accumulated gradient-based input waveform-like signal that maximizes the activation of a filter in the layers. To effectively find the filter characteristics, we set the input size to 729 samples, close to a typical frame size.}}
    \label{fig:filters}
\end{figure}

@@

\begin{table}[ht]
\centering
\small
\begin{tabularx}{\textwidth}{
  >{\centering\arraybackslash\hsize=0.4\hsize}X
  >{\centering\arraybackslash\hsize=0.2\hsize}X
  >{\centering\arraybackslash\hsize=0.2\hsize}X
  >{\centering\arraybackslash\hsize=0.2\hsize}X}
\toprule
\thead{\textbf{Layer Type}} & \thead{\textbf{In Channels}} & \thead{\textbf{Out Channels}} & \thead{\textbf{Num. of layers}} \\
\midrule
Conv + ReLU & 1 & 128 & 1 \\
Conv + BatchNorm + ReLU + MaxPool & 128 & 128 & 2 \\
 & 128 & 256 & 1 \\
 & 256 & 256 & 6 \\
 & 256 & 512 & 1 \\
Conv + BatchNorm + ReLU + AvgPool & 512 & 512 & 1 \\
Fully connected layer & 512 & 128 & 1 \\
\bottomrule
\end{tabularx}
\caption[SampleCNN layer specifications]{\small{Layer specifications for our SampleCNN model implementation; extended from \cite{CLMR2021}.}}
\label{tab:samplecnntable}
\end{table}
